SAT Competition 2020\tnoteref{title}

### 2020-12-10 paper/main.tex
actualy Sect 2 is a more general overview

@@

\begin{abstract}
SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors can compete. 
Another novelty is the application-specific sub-track of the main track, where solvers compete in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
We use new tools to select and distribute benchmark instances and their attributes. 
In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
\end{abstract}

@@

In Section~\ref{sec:tracks}, we start with a detailed description of the competition tracks and their purpose. 
Section~\ref{sec:instances} contains an overview on the selected benchmark instances and details about the selection process. 
In Section~\ref{sec:results}, we present the competition results alongside a survey on the winning strategies of the award winning solvers. 
A meta-analysis of these results follows in Section~\ref{sec:analysis}, and we conclude with Section~\ref{sec:conclusion}.

\section{Descriptions of Tracks}
\label{sec:tracks}

\subsection{Main Tracks}

\subsection{Incremental Library Track}

@@

In Kissat forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
For irredundant clauses forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.

@@

To the Main track, the solver was submitted in two variants, with and without LSIDS~\cite{Shaw:2020:LSIDS}, which is a phase selection heuristic similar to VSIDS and if active it is used whenever backtracking is chronological~\cite{Nadel:2018:CBT}. 
On top of that, CryptoMiniSat is periodically switching between polarity saving and stable phases~\cite{Biere:SC2019}.

By tight integration of CCAnr~\cite{Cai:2015:CCAnr}, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies SLS and CDCL in a unique way. 
They run local search for a short period of time in regular intervals and (just in case SLS finds no solution) change the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCal~\cite{Biere:SC2019}.
Moreover, they bump VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy~\cite{Soos:SC2020}.

SLS is tightly integrated and thus is aware of changes occurring during inprocessing. 
Inprocessing now also include ternary resolution and vivification is used a lot more~\cite{ChuMinLi:2020:Vivification}. 
All modifictions in CrytoMiniSat are fully integrated with resprect to incremental use-cases including the use of assumptions.

@@

\subsubsection{P-MCOMSPS-STR} three awards

@@

>>>>

\address[ctu] {
Czech Technical University in Prague, Czech Republic\\
\url{martin.suda@cvut.cz}\\[1em]
}

@@

\begin{abstract}
SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors could compete. 
Another novelty was the application-specific sub-track of the main track, 
where solvers competed in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
We used new tools to select and distribute benchmark instances and their attributes. 
In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
\end{abstract}

@@

In Section~\ref{sec:overview}, we start with an overview of the competition,
including detailed description of the competition tracks and their purpose,
the general rules and the used computing environment.
Section~\ref{sec:instances} contains an overview on the selected benchmark instances and details about the selection process. 
In Section~\ref{sec:results}, we present the competition results alongside a survey on the winning strategies of the award winning solvers. 
A meta-analysis of these results follows in Section~\ref{sec:analysis}, and we conclude with Section~\ref{sec:conclusion}.

\section{Overview of the competition}
\label{sec:overview}

\subsection{Competition tracks}

\subsubsection{Main Tracks}

\subsubsection{Incremental Library Track}

\subsubsection{Parallel Track}

\subsubsection{Cloud Track}

\subsection{Rules, ranking, etc.}

\subsection{Computing environments}

@@

In Kissat, forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
For irredundant clauses, forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.

@@

To the Main track, the solver was submitted in two variants, with and without LSIDS~\cite{Shaw:2020:LSIDS},
which is a phase selection heuristic similar to VSIDS and, if active, it is used whenever backtracking is chronological~\cite{Nadel:2018:CBT}. On top of that, CryptoMiniSat is periodically switching between polarity saving and stable phases~\cite{Biere:SC2019}.

By tight integration of CCAnr~\cite{Cai:2015:CCAnr}, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies, SLS and CDCL, in a unique way. 
The solver runs local search for a short period of time in regular intervals and (just in case SLS finds no solution)
changes the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCal~\cite{Biere:SC2019}.
Moreover, it bumps VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy~\cite{Soos:SC2020}.

SLS is tightly integrated and thus is aware of changes occurring during inprocessing. 
Inprocessing now also includes ternary resolution and vivification is used a lot more~\cite{ChuMinLi:2020:Vivification}. 
All modifictions in CrytoMiniSat are fully integrated with resprect to incremental use-cases including the use of assumptions.

@@

\subsubsection{P-MCOMSPS-STR}

P-MCOMSPS-STR is built from the Painless framework~\cite{Frioux:2017:Painless} for solver parallization and uses the MapleCOMSPS solver~\cite{Liang:2017:Maplecomsps} as a building block. 
The authors submitted a 32 and 64 core version and won 3 awards, first place in the overall ranking, first place in the SAT ranking and second in the UNSAT ranking. 
The 64 core version performed slightly worse than the 32 core version in the overall ranking, and that gap is bigger for the SAT-only ranking and worst for the UNSAT-only ranking, such that in the separate rankings only the 32 core version is responsible for winning the prices.

The painless framework uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrenct data-structures, such that implementations within the framework boil down to implementing parallelization and clause sharing strategies.

In the submitted version of P-MCOMSPS-STR, diversification is done via diverse fixed configurations of branching strategies (LRB and VSIDS) and sparse random intialization of variable polarities like in~\cite{Balyo:2015:Hordesat}. 
One instance of their ``sequential engines'' performs concurrent clause strengtheing as described in~\cite{Wieringa:2013:CCS} and another single instance is configured to perform Gaussian eliminiation during preprocessing.

For sharing they use an all-to-all strategy with a regular exchange of a fixed size buffer and a dynamic clause lbd limit.

@@

\section*{Acknowledgements}
Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
the Czech Science Foundataion project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.
